---
title: "Hog"
output: html_document
---

####0. Libraries

```{r}

library(knitr)
library(tidyverse)

```

####1. Aquaculture

Inputs

```{r aquaculture_in_read}

```

```{r aquaculture_in}

```

Functions

```{r aquaculture_fun_read}

```

```{r aquaculture_fun}

```

Outputs

```{r aquaculture_out_read}

```

```{r aquaculture_out}

```

####2. Fishery

Inputs

a. Get inputs from sources. Store in .csv and in the environment.

```{r fishery_in_read, cache = FALSE}

knitr::read_chunk('fi_in.R')

```

```{r fi_in}
```

Functions

b. Build functions and get parameters from math and inputs. 

```{r fishery_fun_read}

print(fi_in)

```

```{r fishery_fun}

```

Outputs

c. Gather up parameters from functions and store.

```{r fishery_out_read}

```

```{r fishery_out}

```

####3. Market

Inputs

```{r market_in_read}

```

```{r market_in}

```

Functions

```{r market_fun_read}

```

```{r market_fun}

```

Outputs

```{r market_out_read}

```

```{r market_out}

```

####4. Hog Parameters

Name 'em, join 'em, make 'em available.

```{r par}

```

####5. Hog Function

```{r fun}

```

####6. Hog Runs

```{r run}

```

####7. Hog Outputs

Tables and visualization.

```{r vis}

```

```{r tab}

```


